Figures

### 2019-05-30 figures/07_model-selection.Rmd
cleanup stream buffer scatter plot
make residual dotplot

# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
#                 summarize(
#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
#                            lagoslakeid), 
#                   tp = median(tp, na.rm = TRUE), 
#                   chla = median(chla, na.rm = TRUE)), 
#                 by = "lagoslakeid") %>%
#   tidyr::drop_na()

@@

```{r model_fitting, echo=FALSE}
library(brms)
library(tidybayes)
library(modelr)

@@

```{r model_diagnostics_basics, echo=FALSE, fig.height=2}
# get_variables(fit0)
plot(fit0, pars = "ag")
```

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_ag) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))

@@

```{r signif_map, echo=FALSE}
ggplot() + 
  geom_sf(data = hu4) +
  geom_sf(data = hu4_signif, color = "red")
```

>>>>

# setwd("figures")
ids <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
#                 summarize(

#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
#                            lagoslakeid), 
#                   tp = median(tp, na.rm = TRUE), 
#                   chla = median(chla, na.rm = TRUE)), 
#                 by = "lagoslakeid") %>%
#   tidyr::drop_na()

@@

```{r residual_dotplot, echo=FALSE}
fit <- readRDS("data/mcmc/re/tn_corn")

get_residuals <- function(model, threshold = 0.1){
  # model <- re_brms[[1]]
  model$res_med <- dt %>%
    add_residual_draws(model) %>%
    group_by(lagoslakeid) %>%
    summarize(.residual_median = median(.residual)) %>%
    left_join(dplyr::select(lg$locus, lagoslakeid, nhd_lat, nhd_long),
              by = "lagoslakeid")

  model$res_med <- dt %>%
    add_fitted_draws(model) %>%
    group_by(lagoslakeid) %>%
    summarize(.value_median = median(.value)) %>%
    right_join(model$res_med, by = "lagoslakeid")

  model$res_test <- abs(
    median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
  model
}
lg <- lagosne_load()
fit <- get_residuals(fit)

states_lg <- 
  state_sf()[unlist(lapply(st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)), function(x) length(x) > 0)),]

ggplot() + 
  geom_sf(data = states_lg) +
  geom_sf(data = LAGOSNE::coordinatize(fit$res_med), 
          aes(color = .residual_median), size = 0.8) +
  coord_sf(datum = NA) +
  theme_void() + 
  scale_color_gradient2() +
  labs(color = "tn_corn model residuals")

```{r model_fitting, echo=FALSE, eval=FALSE}
library(brms)
library(tidybayes)
library(modelr)

@@

```{r model_diagnostics_basics, echo=FALSE, fig.height=2, eval=FALSE}
# get_variables(fit0)
plot(fit0, pars = "ag")
```

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_ag) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))

@@

```{r signif_map, echo=FALSE, eval=FALSE}
ggplot() + 
  geom_sf(data = hu4) +
  geom_sf(data = hu4_signif, color = "red")
```
